quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2024-06-23 paper-quollr.Rmd
Add visualization introduction paragraph

>>>>

The package provides five basic visualizations which includes one to visualize the full hexagonal grid in $2\text{-}D$, three visualizations related to the $2\text{-}D$ model (static visualizations), and one related to the $p\text{-}D$ model (dynamic visualization). Each visualization can be generated using its respective function, as described in this section.
